---
title: "VAST"
author: "Hume Dickie"
date: "May 22, 2017"
output: html_document
---

\\Meta stuff
From earlier code I didn't save, the park is definitely a summer location. There is a plot in the img folder though.











```{r setup}
library(magrittr)
library(ggplot2)

run.pagerank <- FALSE

alreadyRun.timestamp <- FALSE
```


Pagerank Results!
  1: GG7
  2: G8, G4, G3, GG6
  3: GG2
  4: G5
  5: G7
  6: G2
  7: GG1
  8: GG3, GG0, C6, GG5, C1, E4, E2, C8, G6
  9: G0
  10: G1
  11: GG4, E3, E0
  12: C3, C4, C0, C2, E1
  13: R4,C5
  14: R2
  15: R0
  16: R6
  17: R7
  18: R1
  19: R5, R3, C7, Base

```{r iGraphPageRank}
if (run.pagerank) {
  setwd("C:/Users/Hume Dickie/Desktop/Github/Mini-Challenge-1/data/")
  network <- read.csv("matrix.csv")
  network <- network[,-1]
  
  
  for (i in 1:40) {
    for (j in i:40) {
      network[[i]][[j]] <- network[[j]][[i]]
    }
  }
  
  
  network.matrix <- as.matrix(network)
  
  library(igraph)
  
  g <- graph_from_adjacency_matrix(network.matrix,"undirected",diag = FALSE)
  
  page_rank(g)
  pagerank.results <- sort(page_rank(g)[[1]]) %>% rev()
  plot(1:40,pagerank.results)
}
```

```{r loadData}
setwd("C:/Users/Hume Dickie/Desktop/Github/Mini-Challenge-1/data")
sensor <- read.csv("Lekagul Sensor Data.csv", stringsAsFactors = FALSE)
#View(sensor)

timestamp.raw <- sensor[,1]
timestamp <- rep(list(),dim(sensor)[1])

#just to keep me from accidentally rerunning this bc it takes SO long
print("Converting timestamp strings to timestamp objects.")
if (!alreadyRun.timestamp) {
  for (i in seq_along(timestamp.raw)) {
    if (i %% 10000 == 0) {
      print(i/dim(sensor)[1])
    }
    timestamp[[i]] <- strptime(timestamp.raw[[i]],"%m/%d/%Y %H:%M")
  }
  alreadyRun.timestamp <- TRUE
  
  #save(timestamp,"timestamp",file="timestamp-obj.RData")
}

sensor$Timestamp <- timestamp
sensor.ordered <- sensor[order(timestamp),]
View(sensor)
```




Relative popularity of entrances (low to high): 3, 2, 4, 0, 1
                                      Expected: 2, 4, 0, 3, 1
                                      
3 is the only mismatch!
\\
Campsite popularity:
real: 8,5,4,6,3,2,7,0,1
xpctd:6,1,8,3,0,4,2,5,7

1 is a lot less popular, 5 is a lot more popular

\\
```{r pagerankVersusReality}

activity.order <- sensor$gate.name %>% table() %>% sort() %>% names() %>% rev()
pagerank.order <- pagerank.results %>% sort() %>% names() %>% rev()

look.for.nonrandomness <- as.data.frame(cbind(pagerank.order,activity.order))
#not sure on the best way to use this. It's most meaningful at the ends but muddier in the middles
```




```{r loadPaths}
setwd("C:/Users/Hume Dickie/Desktop/Github/Mini-Challenge-1/output/")
labels = c("ID","neveredEntered","enterTime","length","totalTime")
for (i in 1:69) {
  labels <- c(labels,paste("N",i,sep=""),paste("dt",i,sep=""))
}
labels <- c(labels,"N70")
paths <- read.table("abbrev-paths.txt",col.names = labels,fill = TRUE,sep=";",row.names=NULL)
```



Patterns:
  Thru traffic
  Rangers
  Campers
  Weird car

There is a weird car!!! It entered the park at 2015-06-05 14:57:59 and NEVER LEFT
```{r classificationByInspection}

weirdCar.path <- paths[16414,]
weirdCar.id <- "20155705025759-63"

weirdCar.sensor <- sensor[which(sensor$car.id == weirdCar.id),]





#ranger path length distro
ranger.path.distro <- list()
paths.start.base <- paths[which(paths$N1 == "B"),]
for (i in 1:49) {
  currLab <- paste("N",i,sep="")
  ranger.path.distro[[i]] <- dim(paths.start.base[which(paths.start.base[currLab] != ""),])[1]
}

#all minus ranger distro (for comparison)
path.minus.ranger.distro <- list()
paths.minus.rangers <- paths[-which(paths$N1 == "B"),]
for (i in 1:49){
  currLab <- paste("N",i,sep="")
  path.minus.ranger.distro[[i]] <- dim(paths.minus.rangers[which(paths.minus.rangers[currLab] != ""),])[1]
}

traffic <- paths[which(paths$length == 2),]
traffic.table <- table(traffic$N1,traffic$N2)
#all entered through entrances, but B shows up with zero for some reason
#end points are more diverse and there are a lot more entries showning up w 0

```

All paths 28 or longer are rangers (except that 1 creepy car)
```{r takeaways}
#On average, rangers have much longer paths than the overall population of visitors
#Note that the y-axes are very different!
par(mfrow=c(2,1))
plot(1:27,path.minus.ranger.distro[1:27])
plot(1:27,ranger.path.distro[1:27])
```


```{r carsStillInPark}
setwd("C:/Users/Hume Dickie/Desktop/Github/Mini-Challenge-1/data/")
activeCars <- read.table("activeCars.txt",row.names = NULL)
activeCars <- as.data.frame(activeCars)
names(activeCars) <- "car.id"

mysteryCars <- paths[is.element(paths$ID,activeCars$car.id),] #all at the end. They just haven't left the park yet!
```

```{r neverEntered}
neverEntered <- paths[paths$neveredEntered,]
View(neverEntered)

#nobody! Strange?
```

```{r look}
setwd("C:/Users/Hume Dickie/Desktop/Github/Mini-Challenge-1/output/")
indi <- read.csv("individual-records.txt",sep=";")
```

```{r temp}
run <- ""
for (n in names(paths)){
  run <- paste(run,n,sep=",")
}
```

WOAH THIS IS CRAZY. Paths jointed to the entry!!!
```{r LegakulSensorDate_Join1}
setwd("C:/Users/Hume Dickie/Desktop/Github/Mini-Challenge-1/data/")
LegSense <- read.csv("Lekagul Sensor Data.csv")
```





preliminary results:
C8  | SIZE = 925
C3  | SIZE = 495
C2  | SIZE = 805
C1  | SIZE = 14
C0  | SIZE = 480
C7  | SIZE = 526
C6  | SIZE = 403
C5  | SIZE = 1186
C4  | SIZE = 960

Has not been double checked!

```{r groupDetection}
setwd("C:/Users/Hume Dickie/Desktop/Github/Mini-Challenge-1/output/")
campRecs <- read.csv("campsite-records.txt",sep=",",stringsAsFactors = FALSE)
campRecs <- campRecs[order(campRecs$startTimestamp),]

#write.csv(campRecs,"campsite-records-sorted.csv")
```


just real quick
```{r plotCampsiteFrequency}
camps <- c("C8","C3","C2","C1","C0","C7","C6","C5","C4")
vals <- c(925,495,805,14,480,526,403,1186,960)

plt <- as.data.frame(cbind(camps,vals))

library(ggplot2)
ggplot(data = plt) + 
  geom_line()
```

```{r whatIsPopulation}
setwd("C:/Users/Hume Dickie/Desktop/Github/Mini-Challenge-1/output/")
popTimeSeries <- read.csv("campsite-population-time-series.txt")
#View(popTimeSeries)

C6 <- popTimeSeries[which(popTimeSeries$gate=="C6"),]
names(popTimeSeries)
```

```{r sortCampRecs}
times.arrive.raw <- campRecs.C6$startTimestamp
times.leave.raw <- campRecs.C6$endTimestamp

for (i in seq_along(times.raw)) {
  if (i %% 10000 == 0) {
    print(i/dim(sensor)[1])
  }
  timestamp[[i]] <- strptime(timestamp.raw[[i]],"%m/%d/%Y %H:%M")
}
```

Gotta crawl through it

20155705025759-63 is the only car in C6 an odd number of times
```{r validateSuspiciousGroupPlot}
setwd("C:/Users/Hume Dickie/Desktop/Github/Mini-Challenge-1/output/")
popTimeSeries <- read.csv("campsite-population-time-series.txt")

C6 <- popTimeSeries[which(popTimeSeries$gate=="C6"),]
par(mfrow=c(2,1))
plot(1:917,C6$population)
lines(1:917,C6$population)
plot(1:10,C6[1:10,"population"])
lines(1:10,C6[1:10,"population"])

ftable(table(C6$car.id))

car.odd.times <- C6[which(C6$car.id=="20155705025759-63"),]
```